---
title: "Files-Folders-Homework"
author: "Kelsey Martin"
date: "2024-02-04"
output: html_document
---


```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/GitHub/CSU_CM515_2024/modules/03_Files_and_Folders")
library("fs")

```

## Assignment for Module 3: Files & Folders

To recieve full credit, complete all sections. Upload your knitted Rmd in html, not Rmd, to Canvas. If you are having issues knitting your Rmd, email Shady (shady.kuster@colostate.edu), email David (david.king@colostate.edu), or attend coding club this Friday for help. I'm (shady) happy to meet in person, too, if that is more helpful, but I am likely unable to attend coding club due to prior commitments.  

This assignment is due *February 14th at 10AM*. 


## Conceptual Questions

1) What is the difference between an absolute path and a relative path?

Absolute path is the full/complete directions to a file or folder, while a relative path gives the directions based on current location within a directory.

2) When might you use a relative or an absolute path?

You would use it when you are trying to direct R to a location, like to read or write a file. When you use a relative path you would use the "~" symbol to indicate the directions start at the CWD.

*QUESTION: Are there some cases where you have to use an absolute or relative path (and the other wouldn't work)?*

3) If you get the error "cannot open file 'example.csv': No such file or directory", what things should you check first?

You should check to make sure your working directory is where you think it is (`getwd()`), check the names and spelling and cases of the directions you gave as well.

## Applied Questions

4) Create the following directory system. Use dir_tree() to output the directory structure of the directory you made. 

Within your cwd (change to a new, empty folder):
ExFolder is empty
Plant-Genera contains two directories: 1) Silene and 2) Arabidopsis
Projects contains a directory called Linkage and two text files: 1) to-do.txt and 2) project-ideas.txt

```{r}
#Question 4
message1<- "grade 300 exams, run 12 6 hour experiments, study for 27  hours, somehow get sleep"
message2<-"Projects:\n cabin in the woods\n electritian certification\n win lottery"
write(message1, "Exfolder/Projects/Linkage/to-do.txt")
write(message2, "Exfolder/Projects/Linkage/project-ideas.txt")
```

5) Make sure you have downloaded the HomeworkAssignmentInput.txt file from Canvas. 
a) without modifying the code below and keeping your cwd the same as before (do not modify it), successfully run the following code chunk:

```{r}
#Question 5a - do not edit any of this code
paste(readLines("HomeworkAssignmentInput.txt"))

dir_tree(".")

```

b) copy the file to the Silene directory, and read in the file from that directory, keeping your cwd the same as the previous question. 

```{r}
#Question 5b 
paste(readLines("Exfolder/Plants-Genera/Silene/HomeworkAssignmentInput.txt")) #fill in path here

dir_tree(".") #keep this here

```

c) now, change your working directory to be able to read the file from the Silene directory.

```{r}
#Question 5c
setwd("~/GitHub/CSU_CM515_2024/modules/03_Files_and_Folders/Exfolder/Plants-Genera/Silene")
#add what you need to here

paste(readLines("HomeworkAssignmentInput.txt")) #do not change this line

dir_tree(".") #keep this here
```

