---
title: "2024-04-15_groupproject"
author: "Kelsey Martin"
date: "2024-04-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries and dataset
```{r}
library(ggplot2)
library(ggthemes)
MutationRate = read.delim ("MutationRate.txt")

```

graph:
```{r}
groupgraph<- ggplot (data=MutationRate, aes(x=Genotype, y=MutationRate, color=Genotype))+
geom_point(alpha=0.5, size=2)+
  ylab("Log10 Mutation Rate")+
scale_y_log10()+
facet_grid(MutationType~Genome)+
  theme_stata()
```
We decided to do geom_point() because we only have three replicates, so it would show up well as a scatter plot.
We also changed this to a log scale because the data was spread out and some things were lost at the linear scale, everything was all clustered at the bottom and hard to see.
We then faceted by both genome and mutation type using facet grid, so we can visualize the differences in genome and types of mutations that are happening.



Saving graph:

```{r}
pdf ("2024-04015_DataViz_GroupGraph.pdf")  
groupgraph  
dev.off()
```